Clustering in a hyperbolic model of complex networks.

### 2019-03-21 clustering_infinite_model.tex
beta integral detail in computation for alpha =1

\begin{proof}
\TM{\RD{Warning!} this has not been properly proofread by me, or anyone else.}
We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
\begin{align*}
&P_\alpha(y_0(z_0)) \\
&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+\frac{1}{\alpha-1}(s_3(\alpha,z_0)+s_4(\alpha,z_0)) 
+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
\end{align*}
where
\begin{align*}
s_1(\alpha,z_0) &= -\frac{1}{8 \alpha}\\
s_2(\alpha,z_0) &= (\alpha-1/2)z_0 \\
s_3(\alpha,z_0) &= - \frac{(\alpha - 1/2)^2 z_0^2}{4}\\
s_4(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha}\\
s_5(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha}\\
s_6(\alpha,z_0) &= \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} \\
s_7(\alpha,z_0) &= - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4}
\end{align*}
Now, we consider the functions $s_i(\alpha) = s_i(\alpha,z_0)$ as functions of $\alpha$ only and compute their Taylor 
expansion at $\alpha=1$, for $i\in \{1,2,5,6,7\}$ up to linear and for $i\in \{3,4\}$ up to quadratic order, i.e. we 
write $s_i(\alpha) = s_i(1)+s_i'(1)(\alpha-1)+o(\alpha-1)$ for $i\in \{1,2,5,6,7\}$ and 
$s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
\begin{align*}
&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
\end{align*}
In order to continue, we compute:
\begin{align*}
s_1(\alpha) &=-\frac{1}{8}+\frac{1}{8}(\alpha-1)+o(\alpha-1) \\
s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+o (\alpha-1)\\
s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+o(\alpha-1)\\
s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
\end{align*}
Based on this we see that
\begin{align*}
s_3(1)+s_4(1)=-\frac{1}{16}z_0^2+\frac{1}{16}z_0^2 =0
\end{align*}
and
\begin{align*}
&\sum_{i\in \{1,2,5,6,7\}} s_i(1) + s_3'(1)+s_4'(1) \\
&= -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) 
+\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 
-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ 
&\hspace{50pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 \\
&=0
\end{align*}
Finally, it follows that
\begin{align*}
P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
\end{align*}
Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by
\begin{align*}
&\sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))\\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} 
		\ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
		+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}\dd t \\
	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
		-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) 
		+ \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) \\
	&\hspace{10pt}+\frac{1}{2}z_0 \Li_2(z_0)) - z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
	&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 \\
	&\hspace{10pt}- \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) -\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
\end{align*}
where we used that
\begin{align*}
	z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1} \dd t
	&= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2),
\end{align*}
and
\begin{align*}
	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt\\
	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
\end{align*}
By expanding the squares and collecting terms, the last expression can be simplified to
\begin{align*}
&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) + 
z_0^2 \left(-7/8 - \frac{\ln(2)^2+2\Li_2(1/2) + 2\Li_2(1)}{4} \right) + 
\frac{1}{2}z_0^2 \Li_2(z) \\
=&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z)
\end{align*}
which finishes the computation.
\end{proof}

>>>>

\begin{proof}
\TM{\RD{Warning!} this has not been properly proofread by me, or anyone else.}
We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
\begin{align*}
&P_\alpha(y_0(z_0)) \\
&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+\frac{1}{\alpha-1}(s_3(\alpha,z_0)+s_4(\alpha,z_0)) 
+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
\end{align*}
where
\begin{align*}
s_1(\alpha,z_0) &= -\frac{1}{8 \alpha}\\
s_2(\alpha,z_0) &= (\alpha-1/2)z_0 \\
s_3(\alpha,z_0) &= - \frac{(\alpha - 1/2)^2 z_0^2}{4}\\
s_4(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha}\\
s_5(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha}\\
s_6(\alpha,z_0) &= \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} \\
s_7(\alpha,z_0) &= - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4}
\end{align*}
Now, we consider the functions $s_i(\alpha) = s_i(\alpha,z_0)$ as functions of $\alpha$ only and compute their Taylor 
expansion at $\alpha=1$, for $i\in \{1,2,5,6,7\}$ up to linear and for $i\in \{3,4\}$ up to quadratic order, i.e. we 
write $s_i(\alpha) = s_i(1)+s_i'(1)(\alpha-1)+o(\alpha-1)$ for $i\in \{1,2,5,6,7\}$ and 
$s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
\begin{align*}
&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
\end{align*}
In order to continue, we compute:
\begin{align*}
s_1(\alpha) &=-\frac{1}{8}+\frac{1}{8}(\alpha-1)+o(\alpha-1) \\
s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+o (\alpha-1)\\
s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+o(\alpha-1)\\
s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
\end{align*}
Based on this we see that
\begin{align*}
s_3(1)+s_4(1)=-\frac{1}{16}z_0^2+\frac{1}{16}z_0^2 =0
\end{align*}
and
\begin{align*}
&\sum_{i\in \{1,2,5,6,7\}} s_i(1) + s_3'(1)+s_4'(1) \\
&= -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) 
+\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\left(\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2\right) 
+\left(-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2\right) \\ 
&\hspace{50pt}+\left(\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}\right)+\left(\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0\right) \\
&=0
\end{align*}
using that %$B^-(\frac{1}{2};3,0)=-\frac{5}{8}+\ln 2$ and $B^-(1-z_0;2,-1)=-1+z_0^{-1}+\ln z_0$.
\begin{align*}
B^-(\frac{1}{2};3,0)&=\int_0^\frac{1}{2}t^2(1-t)^-1dt=\int_\frac{1}{2}^1 (1-s)^2 s^{-1}ds\\
&=\int_\frac{1}{2}^1 s^{-1}-2+sds = -2+\frac{1}{2}-\ln\frac{1}{2}+1-\frac{1}{8}=-\frac{5}{8}+\ln 2
\end{align*}
and
\begin{align*}
B^-(1-z_0;2,-1)&=\int_0^{1-z_0} t(1-t)^{-2}dt = \int_{z_0}^1 (1-s)s^{-2}ds \\
&=\int_{z_0}^1 s^{-2}-s^{-1}ds = -1+z_0^{-1}+\ln z_0.
\end{align*}

Finally, it follows that
\begin{align*}
P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
\end{align*}
Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by
\begin{align*}
&\sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))\\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} 
		\ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
		+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}\dd t \\
	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
		-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) 
		+ \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) \\
	&\hspace{10pt}+\frac{1}{2}z_0 \Li_2(z_0)) - z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
	&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 \\
	&\hspace{10pt}- \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) -\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
\end{align*}
where we used that
\begin{align*}
	z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1} \dd t
	&= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2),
\end{align*}
and
\begin{align*}
	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt\\
	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
\end{align*}
By expanding the squares and collecting terms, the last expression can be simplified to
\begin{align*}
&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) + 
z_0^2 \left(-7/8 - \frac{\ln(2)^2+2\Li_2(1/2) + 2\Li_2(1)}{4} \right) + 
\frac{1}{2}z_0^2 \Li_2(z) \\
=&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z)
\end{align*}
which finishes the computation.
\end{proof}
